---
title: "porteretal.pilot1"
author: "Camilla"
date: "2/28/2017"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
```


```{r download pilot data}
pilot1= read_csv('/Users/camilla/Documents/Winter 17/Psych254/Porter-etal2016/experiment/pilot1data.csv')
```


From the paper (re: LIB manipulation checks): 

"As expected, participants in
the favorable-LIB condition believed that Peter was more
likely to be helpful in the future (M = 70.29%, SD = 23.58)
than did participants in the unfavorable-LIB condition
(M = 57.83%, SD = 24.08), t(86) = 2.45, p = .016, d = 0.53.
Similarly, participants in the favorable-LIB condition indicated
that Peter was less likely to be rude in the future
(M = 33.67%, SD = 25.48) compared with participants in
the unfavorable-LIB condition (M = 53.93%, SD = 25.22),
t(86) = 3.73, p < .001, d = 0.80."

```{r manipulation checks}
#condition variable
pilot1 = pilot1 %>%
  slice(3:7) %>%
  mutate(condition= ifelse(is.na(LIB_DV) , "ULIB", "LIB"))
pilot1$condition

#mean perception of peter as helpful & rude
pilot1$MCfuture_helpful_1=as.numeric(pilot1$MCfuture_helpful_1)
pilot1$MCfuture_rude_1=as.numeric(pilot1$MCfuture_rude_1)

pilot1 %>%
  summarise(meanhelp=mean(MCfuture_helpful_1)) 

pilot1 %>%
  summarise(meanrude=mean(MCfuture_rude_1))

#MC question: are people perceiving peter to be more rude/helpful based on condition?
summary(lm(MCfuture_rude_1 ~ condition, data=pilot1))
summary(lm(MCfuture_helpful_1 ~ condition, data=pilot1))
```

From the paper (re: main DV analysis): 

"Social category inference. The primary dependent
measure was participants’ inferences regarding the communicator’s
political affiliation. As predicted, participants
in the favorable-LIB condition were significantly more
likely to believe that the communicator was a Democrat,
and thus shared a party affiliation with the target, than
were participants in the unfavorable-LIB condition,
t(86) = 2.89, p = .005, d = 0.62 (Fig. 1). This difference
was not moderated by participants’ self-reported political-
party affiliation or ideological endorsement (ps > .18).
Our findings suggested initial support for our hypothesis
that individuals can infer a communicator’s social identity
from his or her language, regardless of their own social
identity"

```{r social category inference - MAIN DV}
pilot1[is.na(pilot1)] = ''
#creating new 'social identity perception' variable
pilot1=pilot1%>%
  mutate(peterID=paste(LIB_DV, ULIB_DV))

#does LIB condition impact people's perceptions of Peter's identity? (1=definitely a democrat, 7=definitely a republican)
summary(lm(peterID ~ condition, data=pilot1))
```

